Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-07 paper/paper.tex
pass on workflow

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, provided on
input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options in correspondence with the input messages
(see Section~\ref{sec:rules-and-packets}). It is worth noting that the
rule produced in this step can include more options than the golden
rule (see Section~\ref{sec:suri-metas-coverage}). Consequently, the
use of that rule could lead, in principle, to false negatives as not
all manifestations of the same attack are identical, \ie{}, the
content of messages for two instantiations of a given attack may
differ. Second, \tname{} generates plausible rules similar to the one
produced in the previous step. It is worth noting that any subset of
the original set of options captures the malicious traffic. As the
generation procedure discards options from the initial rule, it
satisfies the invariant of capturing malicious traffic by
construction. However, the goal of \tname\ is to produce rules that
capture \emph{only} malicious traffic. To achieve that goal, \tname{}
uses benign traffic from public databases to check that the
\nids\ instantiated with a given rule does not capture benign
traffic. The minimization step uses a population-based gradient
descent-like search to find all plausible rules, which are derived
from the rule obtained in the previous step. Third,
\Fix{...elaborate...}

>>>>

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, provided on
input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options in correspondence with the input messages
(see Section~\ref{sec:rules-and-packets}). It is worth noting that the
rule produced in this step can include more options than the golden
rule (see Section~\ref{sec:suri-metas-coverage}). Consequently, the
use of that rule could lead, in principle, to false negatives as not
all manifestations of the same attack are identical. Second, \tname{}
generates plausible rules similar to the one produced in the previous
step. It is worth noting that any subset of the original set of
options captures the malicious traffic. As the generation procedure
discards options from the initial rule, it satisfies the invariant of
capturing malicious traffic by construction. However, the goal of
\tname\ is to produce rules that capture \emph{only} malicious
traffic. To achieve that goal, \tname{} uses benign traffic from
public databases to check that the \nids\ instantiated with a given
rule does not capture benign traffic. The minimization step uses a
population-based gradient descent-like search to find all plausible
rules, which are derived from the rule obtained in the previous
step. Third, uses several heuristic functions derived from a dataset
of rules to rank the rules generated in the previous step.
